A new method to estimate dark matter halo concentrations

### 2015-08-20 paper/article.tex
new density test
rewritten the error part

We use a Metropolis-Hastings algorithm to sample the likelihood
function distribution defined by ${\cal L}(c)=\exp(-\chi^2(c)/2)$
where the $\chi^2(c)$ is written as

@@

For the walk in the Metropolis-Hastings algorithm we used 50000 steps
where each step was randomly generated with a normal distribution
centered around the last step with an standard deviation of
$\sigma=0.03$.
From the $\chi^2$ distribution we find the optimal value of the
concentration and  its associated uncertainty.

@@

Using this data-set we also compare our method against the other two
methods described earlier: using shells to estimate the density as a
function of radius and the maximum circular velocity method.
In the first case we use the same Metropolis-Hastings algorithm we
have in our method to fit the density profile.
In the second method we simply follow the procedure described in
Section \ref{sec:method}

@@

Figure \ref{fig:error} shows the behaviour of $\avg{|D|}$ as a function of
halo particle number for the three different methods to estimate the
concentration.
At fixed particle numbers our method always shows the lowest
$\avg{|D|}$ values compared to the other two methods.
Its accuracy is on the order of $10\%$ for $20$ particles in the halo,
going down to $0.1\%$ for halos with $20000$ particles.
The decrease of $\avg{|D|}$ with increasing particle number $N$ goes
approximately as $\avg{|D|}\propto N^{-1/2}$, which reinforces the hint that
the accuracy of the method is related to a decrease of Poisson
noise.

The second best accuracy is achieved by the method based on the
maximum of the circular velocity.
It also shows a similar behaviour $\avg{|D|}\propto N^{-1/2}$.
Its accuracy is $2-5$ times less than in our method, on the order of
$20\%$ for $20$ particle halos and $0.5\%$ for $20000$ particle halos.
The method based on the direct density fit shows the lowest accuracy
of all methods.
Its average values $\avg{|D|}$ are always between $30\%$ and $50\%$
regardless of the particle number. {\bf Necesitamos entender el
  comportamiento de esto.}

>>>>

We use an Affine Invariant Markov chain Monte Carlo implemented in the python
module emcee by FIXME (dfm et al) to sample the likelihood
function distribution defined by ${\cal L}(c)=\exp(-\chi^2(c)/2)$
where the $\chi^2(c)$ is written as

@@

For the walk in the MCMC algorithm we used the default emcee parameters which
are optimal. From the $\chi^2$ distribution we find the optimal value of the
concentration and  its associated uncertainty.

@@

Using this data-set we also compare our method against the other two
methods described earlier: using shells to estimate the density as a
function of radius and the maximum circular velocity method.
In the first case we use the same MCMC algorithm we
have in our method to fit the density profile.
In the second method we simply follow the procedure described in
Section \ref{sec:method}

@@

Figure \ref{fig:error} shows the behaviour of $\avg{|D|}$ as a function of
halo particle number for the three different methods to estimate the
concentration.

At fixed particle numbers our method almost always shows the lowest
$\avg{|D|}$ values compared to the other two methods.
Its accuracy is on the order of $10\%$ for $20$ particles in the halo,
going down to $0.1\%$ for halos with $20000$ particles.
The decrease of $\avg{|D|}$ with increasing particle number $N$ goes
approximately as $\avg{|D|}\propto N^{-1/2}$, which reinforces the hint that
the accuracy of the method is related to a decrease of Poisson
noise.

The method based on the maximum of the circular velocity shows a similar
behaviour $\avg{|D|}\propto N^{-1/2}$. Its accuracy is $2-5$ times less
than in our method, on the order of $20\%$ for $20$ particle halos and
$0.5\%$ for $20000$ particle halos. The method based on the direct density
fit shows the an intermediate accuracy between the other two methods.
